Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2021-11-19 manuscript/manuscript.Rmd

Our work suggests that crowd forecasts and model-based forecasts have slightly different advantages and may be able to complement each other well. Humans can use information that is hard to input into a model, while model-based approaches can perform more advanced calculations and are more easily scalable. When interpreting outputs it is important to distinguish between projections (which show what would happen in the absence of any events that could change the trend) and “genuine” forecasts (aiming to predict future data points whilst accounting for all factors that might influence them). Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention. Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting real projections from humans may be harder.

>>>>

Our work suggests that crowd forecasts and model-based forecasts have different strengths and may be able to complement each other. When choosing a suitable approach for a given task it is important to take into account how the output will be used. In this work we focused on forecasts (which aim to predict future data points whilst accounting for all factors that might influence them), whereas policy makers might be more interested in projections (which show what would happen in the absence of any events that could change the trend) or scenario modelling. Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention. Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting projections that are not influenced by implicit assumptions about the future from humans may be harder.

### 2021-11-19 manuscript/manuscript.tex

Our work suggests that crowd forecasts and model-based forecasts have slightly different advantages and may be able to complement each other well. Humans can use information that is hard to input into a model, while model-based approaches can perform more advanced calculations and are more easily scalable. When interpreting outputs it is important to distinguish between projections (which show what would happen in the absence of any events that could change the trend) and ``genuine'' forecasts (aiming to predict future data points whilst accounting for all factors that might influence them). Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention. Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting real projections from humans may be harder.

>>>>

Our work suggests that crowd forecasts and model-based forecasts have different strengths and may be able to complement each other. When choosing a suitable approach for a given task it is important to take into account how the output will be used. In this work we focused on forecasts (which aim to predict future data points whilst accounting for all factors that might influence them), whereas policy makers might be more interested in projections (which show what would happen in the absence of any events that could change the trend) or scenario modelling. Forecasts may not be a suitable basis for informing policy decisions, if forecasters already have factored in the expectation of a future intervention. Model-based approaches can be either forecasts or projections depending on the assumptions, whereas eliciting projections that are not influenced by implicit assumptions about the future from humans may be harder.
